Appendix A

### 2020-10-04 appendixA/appendixA.Rmd
Using a different name for the distributions

prms.df %>% 
  mutate(param = str_to_upper(param), 
         dist = str_replace(dist, "exp", "Exponential"),
         dist = str_replace(dist, "gamma", "Gamma"),
         dist = str_replace(dist, "weibull", "Weibull"),
         dist = str_replace(dist, "lnorm", "Lognormal"),
         data = str_replace(data, "pop", "POP")) %>% 
  mutate(kpars = ifelse(dist == "exp", 1, 2),
         BIC = log(n)*kpars - 2*loglik,
         AIC = 2*kpars - 2*loglik,
         AICc = AIC + (2* kpars * (kpars+1)/(n-kpars-1))) %>% 
  group_by(data) %>% 
  mutate(deltaBIC = signif(BIC - min(BIC), 3),
         deltaAIC = signif(AIC - min(AIC), 3),
         deltaAICc = signif(AICc - min(AICc), 3)) %>% 
  mutate(best_col = ifelse(deltaBIC == 0, "#ffaa00", "black"))-> nice_prms

@@

$$AIC{_{indlevel}} = 2\cdot \sum \left ( number parameters \right ) + 2\cdot \sum \left ( negative log likelihood \right )$$

@@

$$BIC_{indlevel} = \ln{\sum observations} \cdot \sum{number parameters} + 2\cdot \sum {negative log likelihood}$$

```{r}
all_indiv_prms <- prms.df %>% 
  mutate(kpars = ifelse(dist == "exp", 1, 2),
         BIC = log(n)*kpars - 2*loglik,
         AIC = 2*kpars - 2*loglik,
         AICc = AIC + (2* kpars * (kpars+1)/(n-kpars-1))) %>% 
  group_by(data) %>% 
  mutate(deltaBIC = signif(BIC - min(BIC), 3),
         deltaAIC = signif(AIC - min(AIC), 3),
         deltaAICc = signif(AICc - min(AICc), 3))
#saveRDS(all_indiv_prms, file = "outputs/prms_indiv.RDS")

prms.df %>% 
  dplyr::select(., loglik, n, dist, data) %>% 
  distinct() %>% 
  mutate(kpars = ifelse(dist == "exp", 1, 2),
         BIC = log(n)*kpars - 2*loglik,
         AIC = 2*kpars - 2*loglik,
         AICc = AIC + (2* kpars * (kpars+1)/(n-kpars-1))) %>% 
  group_by(data) %>% 
  mutate(deltaBIC = signif(BIC - min(BIC), 3),
         deltaAIC = signif(AIC - min(AIC), 3),
         deltaAICc = signif(AICc - min(AICc), 3)) -> popind.IC

```{r}
popind.IC %>% 
  pivot_longer(., cols = starts_with("delta"), names_to = "ic", values_to = "value") %>% 
  ggplot(., aes(x = ic, y = value, color = dist)) +
  geom_point() +
  facet_wrap(~data, scales = "free")
```

>>>>

prms.df %>% 
  mutate(param = str_to_upper(param), 
         dist = str_replace(dist, "exp", "Exponential"),
         dist = str_replace(dist, "gamma", "Gamma"),
         dist = str_replace(dist, "weibull", "Weibull"),
         dist = str_replace(dist, "lnorm", "Lognormal"),
         data = str_replace(data, "pop", "POP")) %>% 
  mutate(kpars = ifelse(dist == "Exponential", 1, 2),
         BIC = log(n)*kpars - 2*loglik,
         AIC = 2*kpars - 2*loglik,
         AICc = AIC + (2* kpars * (kpars+1)/(n-kpars-1))) %>% 
  group_by(data) %>% 
  mutate(deltaBIC = signif(BIC - min(BIC), 3),
         deltaAIC = signif(AIC - min(AIC), 3),
         deltaAICc = signif(AICc - min(AICc), 3)) %>% 
  mutate(best_col = ifelse(deltaBIC == 0, "#ffaa00", "black"))-> nice_prms

@@

$$AIC{_{indlevel}} = 2\cdot \sum \left ( number parameters \right ) + 2\cdot \sum \left ( -\ln\mathcal{L}() \right )$$

@@

$$BIC_{indlevel} = \ln{\sum observations(samplesize)} \cdot \sum{number parameters} + 2\cdot \sum {negative log likelihood}$$

```{r}
nice_prms %>%
  dplyr::select(., dist, data, deltaBIC, deltaAIC, deltaAICc) %>% 
  distinct() %>% 
  pivot_longer(., cols = starts_with("delta"), names_to = "ic", values_to = "value") %>% 
  ggplot(., aes(x = ic, y = value, color = dist)) +
  geom_point() +
  facet_wrap(~data, scales = "free")
```
